---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

First we have to know which library to use

``` {r library}
library(dplyr)
library(lubridate)
library(ggplot2)
```

## Reading Data

``` {r Read}
RawDataSet<- read.csv("C:/Users/n.taghidoost/Downloads/Compressed/activity.csv")
```

Now we change the class of Date column to be date

```{r DateClass}
RawDataSet$date <- as.Date(RawDataSet$date)
```


## Sum of Steps for Each Day

```{r SumPerDay}
SumPerDay <- RawDataSet %>% group_by(date) %>% summarise(sum(steps,na.rm = TRUE))

colnames(SumPerDay) <- c("Date","TotalSum")
```

We can make histogram with this dataset

```{r FirstPlot}
ggplot(data=SumPerDay,aes(x=TotalSum)) +
  geom_histogram(color="white",bins = 30,fill="orange")+
  geom_vline(aes(xintercept=mean(TotalSum)),color="green") + 
  geom_vline(aes(xintercept=median(TotalSum)),color="blue")+
  ylab("Frequency")
```

### Mean

```{r FirstMean,echo=FALSE}
mean(SumPerDay$TotalSum)

```

### Median

```{r FirstMedian,echo=FALSE}
median(SumPerDay$TotalSum)

```


## Average Steps for Each Interval

```{r SumPerInterval}

SumPerInterval <- RawDataSet %>% group_by(interval) %>% summarise(mean(steps,na.rm = TRUE))
colnames(SumPerInterval) <- c("Interval","AverageSteps")


ggplot(data=SumPerInterval,aes(x=Interval,y=AverageSteps))+
  geom_line(color="steelblue")



```

And here is the interval which has the maximum average steps:

```{r MaxStepsPerInterval, echo=FALSE}

as.data.frame( SumPerInterval[ which.max(SumPerInterval$AverageSteps), ] )

```


Number of null values are 

```{r NumNull,echo=FALSE}

sum(is.na(RawDataSet$steps))

```

Here we fill in the null records with the average of its interval

```{r FillingNulls}

MeanPerInterval <-  RawDataSet  %>%  group_by(interval) %>%
  summarise( mean(steps,na.rm = TRUE) ) %>% data.frame()
  

DataSet_MeanInterval <- data.frame(merge(RawDataSet,MeanPerInterval,by = 'interval' )) 
colnames(DataSet_MeanInterval)[4] <- c("MeanSteps")

NA_Records <- which(is.na(RawDataSet$steps)==TRUE)

RawDataSet[NA_Records,"steps"]= DataSet_MeanInterval[NA_Records,"MeanSteps"]
```

Now again we can make histogram but this time with the filled in values

```{r SecondPlot}

ModifiedSumPerDay <- RawDataSet %>% group_by(date) %>% summarise(sum(steps,na.rm = TRUE)) %>%     data.frame()

colnames(ModifiedSumPerDay) <- c("Date","TotalSum")


ggplot(data=ModifiedSumPerDay,aes(x=TotalSum)) +
  geom_histogram(color="white",bins = 30,fill="orange")+
  geom_vline(aes(xintercept=mean(TotalSum)),color="green") + 
  geom_vline(aes(xintercept=median(TotalSum)),color="blue")+
  theme(legend.position = "right",legend.justification = "top")+
  ylab("Frequency")
```


### Mean

```{r SecondMean,echo=FALSE}
mean(ModifiedSumPerDay$TotalSum)

```

### Median

```{r SecondMedian,echo=FALSE}
median(ModifiedSumPerDay$TotalSum)

```

## Patterns in weekends and weekdays

We can add a factor named "Weekday" to see if the date is weekend or not

```{r WeekdayFactor}

DataSet_MeanInterval <- mutate(DataSet_MeanInterval,
                        weekday = as.factor(ifelse(weekdays(DataSet_MeanInterval$date) %in%
                                  c("Saturday", "Sunday"),"Weekend","Weekday"
                                         ) )
                         )
```


## Average Steps for Each Interval for weekdays and weekends

```{r SumPerIntervalWeekday}

SumPerInterval_Weekday <- DataSet_MeanInterval %>% group_by(interval,weekday) %>% summarise(mean(steps,na.rm = TRUE))
colnames(SumPerInterval_Weekday) <- c("Interval","Weekday","AverageSteps")



ggplot(data=SumPerInterval_Weekday,aes(x=Interval,y=AverageSteps))+
  geom_line(aes(color=Weekday))+facet_grid(Weekday~.)



```